%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Teaching Assistant - Systems Programming}{March 2026 -- Present}
    {University of Washington}{Seattle, Washington}
    \resumeItemListStart
        \resumeItem{Managed autograder infrastructure and coordinated grading distribution for the TA team.}
        \resumeItem{Provided lecture support to professors ensuring content was presented effectively.}
        \resumeItem{Streamlined homework and exercise grading utilizing local LLM to increase grading speed by 33\% }
    \resumeItemListEnd

    \resumeSubheading
    {Lead Developer - MITRE eCTF \& Club Officer}{September 2024 -- Present}
    {Batman's Kitchen - UW Cybersecurity Club}{Seattle, Washington}
    \resumeItemListStart
        \resumeItem{Led the 20+ member programming division for the eCTF team and wrote security-critical embedded software utilizing modern cryptographic techniques and secure design principles to defend against hardware attacks.}
        \resumeItem{Served as a club officer, designing cybersecurity curriculum and providing mentorship through weekly workshops and club-wide CTFs.}
    \resumeItemListEnd

    \resumeSubheading
    {Discovery Intern}{July 2024 -- Aug 2024}
    {Microsoft}{Redmond, Washington}
    \resumeItemListStart
        \resumeItem{Designed and implemented new web pages for ONNXRuntime website (250k monthly visits) using Svelte.JS, DaisyUI, and TailwindCSS to create responsive, scalable, and accessible pages.}
        \resumeItem{Collaborated with stakeholders throughout the development lifecycle to ensure a satisfactory final product.}
    \resumeItemListEnd

    \resumeSubheading
    {Team Captain \& Lead Programmer}{May 2021 -- June 2024}
    {FIRST Tech Challenge Robotics - Hazen Scarabs | FTC 8693}{Renton, Washington}
    \resumeItemListStart
        \resumeItem{Led 15 students in annual robotics challenges and started 12 LEGO League and FTC teams for 200+ underserved students, personally mentoring 4 teams.}
        \resumeItem{Raised \$75,000 by engaging local businesses and advocated to WA legislators to expand CTE funding.}
        \resumeItem{Qualified for WA State Championships 3x, winning control, design, and innovation awards.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
